Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-08-31 paper.Rnw
Added Winterburn Atlas segmentation montage figure

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{algorithm, color, algpseudocode, amsmath, url, geometry, ctable}
\usepackage{titlesec, siunitx, graphicx}
\usepackage[round,authoryear]{natbib}
\usepackage[section]{placeins}  % keep floats in their place.
\usepackage{authblk}            % Listing Author affiliations
\usepackage[hypcap]{caption}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/subfield-montage.pdf}
  \end{centering}
  \caption{Sagittal slices from two subjects showing a comparison of the
  original Winterburn atlas subfield segmentations (at 0.3mm-isotropic voxel
  resolution), the subsampled Winterburn segmentations (at 0.9mm-isotropic
  voxel resolution), and the \mb labels on the subsampled atlas image.}
  \label{fig:subfield-montage}
\end{figure}

\todo[inline]{Figure \ref{fig:subfield-montage}. Show MAGeT segmentations on
BRAVO images.  Also, show coronal/transverse slices and MNI coordinates}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/ADNI1_SNT_MB_montage/montage.pdf}
  \end{centering}
  \caption{SNT \\gs and MAGeT segmentations for 30 ADNI1 subjects (10
  subjects randomly selected from each disease category in the subject pool used
  in Experiment 1). Sagittal slices are shown for subject unlabelled T1-weighted
  anatomical image, SNT \gs label (green), and \mb label (blue). Noted are
  examples of common segmentation idiosyncrasies: 
  {\em (a)} over-estimation of hippocampal head and  
  {\em (b)} translated SNT \gs segmentation; 
  {\em (c)} under-estimation of hippocampal body and
  {\em (d)} improper inclusion of the vestigial hippocampal sulcus by \mb.}
  \label{fig:ADNI-subfields}
\end{figure}

\todo[inline]{Figure \ref{fig:ADNI-subfields}. Show coronal/transverse slices
and MNI coordinates}

@@

\todo[inline]{could we be seeing a ceiling effect... reaching the limit of what
is achievable with a multi-atlas-based segmentation method}

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{algorithm, color, algpseudocode, amsmath, url, geometry, ctable}
\usepackage{titlesec, siunitx, graphicx}
\usepackage[round,authoryear]{natbib}
\usepackage[section]{placeins}   % keep floats in their place.
\usepackage{authblk}             % Listing Author affiliations
\usepackage{rotating}            % rotating figures
\usepackage[hypcap]{caption}

@@

\begin{sidewaysfigure}
    \begin{centering}
      \includegraphics[width=\linewidth]{figure/winterburn-atlas-montage/figure.pdf}
    \end{centering}
    \caption{Detailed subfield segmentation results of a single subject comparing the
    original Winterburn atlas subfield segmentation (at 0.3mm-isotropic voxel
    resolution), the Winterburn segmentation resampled (at 0.9mm-isotropic
    voxel resolution), the \mb segmentation of the subsampled atlas image, and
    the \mb segmentation of a separate T1 BRAVO acquisition of the subject.}
    \label{fig:subfield-montage}
\end{sidewaysfigure}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/ADNI1_SNT_MB_montage/montage.pdf}
  \end{centering}
  \caption{SNT \gs and MAGeT segmentations for 30 ADNI1 subjects (10
  subjects randomly selected from each disease category in the subject pool used
  in Experiment 1). Sagittal slices are shown for subject unlabelled T1-weighted
  anatomical image, SNT \gs label (green), and \mb label (blue). Noted are
  examples of common segmentation idiosyncrasies: 
  {\em (a)} over-estimation of hippocampal head and  
  {\em (b)} translated SNT \gs segmentation; 
  {\em (c)} under-estimation of hippocampal body and
  {\em (d)} improper inclusion of the vestigial hippocampal sulcus by \mb.}
  \label{fig:ADNI-subfields}
\end{figure}

@@
